Timestep Retries for Robust Simulations

### 2022-11-10 retries/paper.tex
Start writing some text for the retry paper

Retries are great \cite{katzzingale:2019}.

>>>>

Multiphysics simulation software is hard to implement robustly. One reason is that
physics modules usually have one or more failure modes, and the code may have
additional failure modes related to the coupling between modules. Some examples of
simulation failure modes in our field of astrophysics include:
\begin{itemize}
  \item Numerical integration failures in the system of ordinary differential equations (ODEs) representing nuclear fusion
  \item Numerical integration successes in coupled ODE systems that nevertheless result in nonphysical outcomes, like mass fraction > 1
  \item Convergence failures in iterative linear solvers, such as those used to solve the Poisson equation
  \item Convergence failures in iterative non-linear solvers, such as those used for radiation diffusion
  \item Failures in non-linear root finding, such as in non-monotonic equations of state
  \item Zones whose local velocity exceeds the CFL hydrodynamic stability criterion given the selected timestep
  \item Negative density in a zone after a hydrodynamic update
\end{itemize}
All of these failure modes (and more) are represented in the simulation code Castro \citep{castro_joss}.
In our experience, any useful science simulation will almost inevitably hit one of these failure modes.

There are (at least) three possible responses to such failures. First, the application can abort and tell the user
to restart from the latest checkpoint with some modified parameters in the hope of making the failure less likely.
This is undesirable because it can be very disruptive to a long-running simulation, and also because it may not be
clear what step will actually resolve the problem. Second, the application can attempt to patch over the issue.
For example, a negative density may be replaced by a small positive density, or a flux limiter could be applied
to prevent it from occurring in the first place \citep{positivity_preserving}. While this can often keep the
simulation going, it creates unphysical distortions in the simulation. Our anecdotal experience is that most
simulation codes use these first two approaches to deal with such failures.

A third approach, which we believe is generally more robust and less distortionary, is to retry a timestep
that encounters one of these failure modes. Typically one will use a smaller $\Delta t$ on the retry, although
other options exist, such as modifying the spatial resolution when using an adaptive mesh. One astrophysics
application that successfully does this, which we drew inspiration from for this work, is the stellar evolution
code MESA \citep{MESA}.
